Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-11-08 trunk/papers/2012-sandwich/CholColloids.tex
Added pics to Nat. Mater. draft
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2234 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig3.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids is inserted into a thermodynamically stable bulk-BPIII (A), and finally subjected to an electric field along the vertical direction (B). The electric field leads to the formation of a honeycomb structure with hexagonal ordering perpendicular to the field direction. 
Structures correspond to $w=0.23$ and $\phi=5\%$ (see Supporting Information
for full list of parameters). }
\end{figure}

>>>>

\begin{figure}
\centerline{
\includegraphics[width=0.35\textwidth]{col_disc_x_run1267.png}
\begin{minipage}[t]{0.17\textwidth}
\vspace*{-4.6cm}
\includegraphics[width=\textwidth]{sq_x_run1267.png}
\includegraphics[width=\textwidth]{sq_y_run1267.png}
\end{minipage}
\includegraphics[width=0.35\textwidth]{col_disc_x_run1341.png}
\begin{minipage}[t]{0.17\textwidth}
\vspace*{-4.6cm}
\includegraphics[width=\textwidth]{sq_x_run1341.png}
\includegraphics[width=\textwidth]{sq_y_run1341.png}
\end{minipage}
}
\caption{Snapshots of the steady states obtained when a dispersion of colloids is inserted into a thermodynamically stable bulk-BPIII (A). The isotropic nature of the state is evident from the structure factor (B, $k_y-k_z$ plane) and (C, $k_x-k_z$ plane). Subjected to an electric field along the vertical x-direction a honeycomb structure forms with hexagonal ordering perpendicular to the field direction (D), (E, $k_y-k_z$ plane) and (F, $k_x-k_z$ plane).     
Structures correspond to $w=0.23$ and $\phi=5\%$ (see Supporting Information
for full list of parameters). }
\end{figure}

### 2013-11-08 trunk/papers/2012-sandwich/support.tex
Added pics to Nat. Mater. draft
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2234 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.95\columnwidth]{support-fig7.pdf}
\end{center}
\caption{Panels A and B as for Fig. 3, but with the disclination lines
removed for clarity. Panel C shows the situation when the field is
switched off: a residual anisotropic structure remains which reflects the
structure induced by the electric field. The electric field direction
when switched on (panel B) is into the plane of the paper and along z.}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.24\columnwidth]{support-fig8a.png}
\includegraphics[width=0.24\columnwidth]{support-fig8b.png}
\includegraphics[width=0.24\columnwidth]{support-fig8c.png}
\includegraphics[width=0.24\columnwidth]{support-fig8d.png}
\end{center}
\caption{Particle distribution during and after switched electric field direction: 
The above images show the ordering with the electric field along the x-direction 
after a previous run that had the field along z. For clarity disclination lines have
been removed. The left panels show the configuration and the structure factor 
while the field is on, whereas the righ panels show the same quantities after 
switch-off. The structure factor data shows wave vectors $k_y, k_z \in [-3\pi/8 , 3\pi/8]$.}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1342.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_z_run1342.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1342.png}
\end{center}
\caption{}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1343.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1344.png}\\
\end{center}
\caption{}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1345.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1347.png}
\end{center}
\caption{}
\end{figure}
